ESI for "Probabilistic determination of the effect of a deep eutectic solvent on the structure of lipid monolayers"

### 2018-06-24 reports/paper.tex
fix uncertainties printing

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{figures/DLPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DPPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
	\caption{The reflectometry profile, scattering length density profile and probability distribution function for each of the three phosphocholine containing lipids, the lower surface concentration is shown in blue while the higher in green; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:lipids}
\end{figure}
The custom model was co-refined for the highest two concentrations of all lipids. The resulting reflectometry profiles, associated scattering length density profiles and the PDF for the head group volume are shown in Figure \ref{fig:lipids}. Table \ref{tab:liptab} gives details of all varying parameters for each lipid, these are given with asymmetric error bars which correspond to a 95 \% confidence interval, the full PDF plots can be found in the ESI. 
\begin{table*}
	\small
	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the phosphocholine reflectometry model. The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn. \ref{equ:tl}. The values of $d_h$ were obtained from the appropriate use of Eqn. \ref{equ:ht}}
	\label{tab:liptab}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllllll}
		\hline
		 & DLPC & & DMPC & & DPPC & & DMPG & \\
		\hline
		Parameter & Conc 4 & Conc 5 & Conc 4 & Conc 5 & Conc 4 & Conc 5 & Conc 4 & Conc 5 \\
		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle4.txt} & \input{../output/dlpc/angle5.txt} & \input{../output/dmpc/angle4.txt} & \input{../output/dmpc/angle5.txt} & \input{../output/dppc/angle4.txt} & \input{../output/dppc/angle5.txt} & \input{../output/dmpg/angle4.txt} & \input{../output/dmpg/angle5.txt} \\
		$d_t$/\AA & \input{../output/dlpc/tail4.txt} & \input{../output/dlpc/tail5.txt} & \input{../output/dlpc/tail4.txt} & \input{../output/dmpc/tail5.txt} & \input{../output/dppc/tail4.txt} & \input{../output/dppc/tail5.txt} & \input{../output/dmpg/tail4.txt} & \input{../output/dmpg/tail5.txt} \\
		$d_h$/\AA & \input{../output/dlpc/head4.txt} & \input{../output/dlpc/head5.txt} & \input{../output/dlpc/head4.txt} & \input{../output/dmpc/head5.txt} & \input{../output/dppc/head4.txt} & \input{../output/dppc/head5.txt} & \input{../output/dmpg/head4.txt} & \input{../output/dmpg/head5.txt} \\
		$\phi_t$/$\times10^{-2}$ & \input{../output/dlpc/solt4.txt} & \input{../output/dlpc/solt5.txt} & \input{../output/dmpc/solt4.txt} & \input{../output/dmpc/solt5.txt} & \input{../output/dppc/solt4.txt} & \input{../output/dppc/solt5.txt} & \input{../output/dmpg/solt4.txt} & \input{../output/dmpg/solt5.txt} \\
		$\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh4.txt} & \input{../output/dlpc/solh5.txt} & \input{../output/dmpc/solh4.txt} & \input{../output/dmpc/solh5.txt} & \input{../output/dppc/solh4.txt} & \input{../output/dppc/solh5.txt} & \input{../output/dmpg/solh4.txt} & \input{../output/dmpg/solh5.txt} \\
		$\sigma_t$/\AA & \input{../output/dlpc/rought4.txt} & \input{../output/dlpc/rought5.txt} & \input{../output/dmpc/rought4.txt} & \input{../output/dmpc/rought5.txt} & \input{../output/dppc/rought4.txt} & \input{../output/dppc/rought5.txt} & \input{../output/dmpg/rought4.txt} & \input{../output/dmpg/rought5.txt} \\
		$\sigma_h$/\AA & \input{../output/dlpc/roughh4.txt} & \input{../output/dlpc/roughh5.txt} & \input{../output/dmpc/roughh4.txt} & \input{../output/dmpc/roughh5.txt} & \input{../output/dppc/roughh4.txt} & \input{../output/dppc/roughh5.txt} & \input{../output/dmpg/roughh4.txt} & \input{../output/dmpg/roughh5.txt} \\
		\hline
	\end{tabular*}
\end{table*}

It can be seen from Table \ref{tab:liptab} that as would be expected, and as found in previous work,\cite{Mohwald1990,Vaknin1991} the thickness of the tail layer increases as the number of carbon atoms in the tail chains increases. Additionally, it is also observed that the value of the chain tilt either decreases, resulting in a tail thickness increase, or remains constant as the surface concentration increases. This indicates that for DLPC and DPPC these two highest surface concentration measurements where at a similar area per molecule, while the area per molecule slightly decreased between the two measurements for DMPC and DPPC. The phenomena of the tail thickness increasing with increasing surface pressure has been note before for DMPC at the air-water interface.{Bayerl1990} Futhermore, as the surface concentration increases, the amount of solvent in the head layer decreases, or stays the same, this would be expected for the head layer becoming more closely-packed and therefore having less space available for solvent.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{figures/DLPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DPPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
	\caption{The reflectometry profile, scattering length density profile and probability distribution function for each of the three phosphocholine containing lipids, the lower surface concentration is shown in blue while the higher in green; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG. The reflectometry and SLD profiles have been offset in the $y$-axis for clarity. Figure files are available under MIT License.\cite{mccluskey_2018}}
	\label{fig:lipids}
\end{figure}
The custom model was co-refined for the highest two concentrations of all lipids. The resulting reflectometry profiles, associated scattering length density profiles and the PDF for the head group volume are shown in Figure \ref{fig:lipids}. Table \ref{tab:liptab} gives details of all varying parameters for each lipid, these are given with asymmetric error bars which correspond to a 95 \% confidence interval, the full PDF plots can be found in the ESI. 
\begin{table*}
	\small
	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the phosphocholine reflectometry model. The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn. \ref{equ:tl}. The values of $d_h$ were obtained from the appropriate use of Eqn. \ref{equ:ht}}
	\label{tab:liptab}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllllll}
		\hline
		 & DLPC & & DMPC & & DPPC & & DMPG & \\
		\hline
		Parameter & Conc 4 & Conc 5 & Conc 4 & Conc 5 & Conc 4 & Conc 5 & Conc 4 & Conc 5 \\
		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle4.txt} & \input{../output/dlpc/angle5.txt} & \input{../output/dmpc/angle4.txt} & \input{../output/dmpc/angle5.txt} & \input{../output/dppc/angle4.txt} & \input{../output/dppc/angle5.txt} & \input{../output/dmpg/angle4.txt} & \input{../output/dmpg/angle5.txt} \\
		$d_t$/\AA & \input{../output/dlpc/tail4.txt} & \input{../output/dlpc/tail5.txt} & \input{../output/dlpc/tail4.txt} & \input{../output/dmpc/tail5.txt} & \input{../output/dppc/tail4.txt} & \input{../output/dppc/tail5.txt} & \input{../output/dmpg/tail4.txt} & \input{../output/dmpg/tail5.txt} \\
		$d_h$/\AA & \input{../output/dlpc/head4.txt} & \input{../output/dlpc/head5.txt} & \input{../output/dlpc/head4.txt} & \input{../output/dmpc/head5.txt} & \input{../output/dppc/head4.txt} & \input{../output/dppc/head5.txt} & \input{../output/dmpg/head4.txt} & \input{../output/dmpg/head5.txt} \\
		$\phi_t$/$\times10^{-2}$ & \input{../output/dlpc/solt4.txt} & \input{../output/dlpc/solt5.txt} & \input{../output/dmpc/solt4.txt} & \input{../output/dmpc/solt5.txt} & \input{../output/dppc/solt4.txt} & \input{../output/dppc/solt5.txt} & \input{../output/dmpg/solt4.txt} & \input{../output/dmpg/solt5.txt} \\
		$\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh4.txt} & \input{../output/dlpc/solh5.txt} & \input{../output/dmpc/solh4.txt} & \input{../output/dmpc/solh5.txt} & \input{../output/dppc/solh4.txt} & \input{../output/dppc/solh5.txt} & \input{../output/dmpg/solh4.txt} & \input{../output/dmpg/solh5.txt} \\
		$\sigma_t$/\AA & \input{../output/dlpc/rought4.txt} & \input{../output/dlpc/rought5.txt} & \input{../output/dmpc/rought4.txt} & \input{../output/dmpc/rought5.txt} & \input{../output/dppc/rought4.txt} & \input{../output/dppc/rought5.txt} & \input{../output/dmpg/rought4.txt} & \input{../output/dmpg/rought5.txt} \\
		$\sigma_h$/\AA & \input{../output/dlpc/roughh4.txt} & \input{../output/dlpc/roughh5.txt} & \input{../output/dmpc/roughh4.txt} & \input{../output/dmpc/roughh5.txt} & \input{../output/dppc/roughh4.txt} & \input{../output/dppc/roughh5.txt} & \input{../output/dmpg/roughh4.txt} & \input{../output/dmpg/roughh5.txt} \\
		\hline
	\end{tabular*}
\end{table*}

It can be seen from Table \ref{tab:liptab} that as would be expected, and as found in previous work,\cite{Mohwald1990,Vaknin1991} the thickness of the tail layer increases as the number of carbon atoms in the tail chains increases. Additionally, it is also observed that the value of the chain tilt either decreases, resulting in a tail thickness increase, or remains constant as the surface concentration increases. This indicates that for DLPC and DPPC these two highest surface concentration measurements where at a similar area per molecule, while the area per molecule slightly decreased between the two measurements for DMPC and DPPC. The phenomena of the tail thickness increasing with increasing surface pressure has been note before for DMPC at the air-water interface.\cite{Bayerl1990} Futhermore, as the surface concentration increases, the amount of solvent in the head layer decreases, or stays the same, this would be expected for the head layer becoming more closely-packed and therefore having less space available for solvent.
